Local Point Spread Function Approximation of High-Rank Hessians in Inverse Problems Governed by PDEs\thanks{Research supported partially by NSF-DMS-CAREER-1654311, NSF-DMS-184026 and NSF-OAC-1550547.}

### 2024-03-06 presentations/siampp24-tucker/talk.tex
small changes

% title, authors, etc:
\title[Local PSF high-rank Hessian approximation]{Local Point Spread Function Approximation of High-Rank Hessians in Inverse Problems Governed by	PDEs\thanks{Research supported
    partially by NSF-DMS-CAREER-1654311 and NSF-OAC-1550547.}}
%\author[{Noemi
%    Petra}]{No\'{e}mi~Petra\inst{1}}

@@

	\begin{itemize}
		\setlength\itemsep{1.0em}
		\item Motivation
		\vspace{0.02in}
		\begin{itemize}
			\setlength\itemsep{1.0em}
			\item Predictive continental scale ice sheet models for anticipating future sea level rise with quantified uncertainties
			\vspace{0.02in}
			\item The need to go beyond ``low rank'' Hessian approximations
		\end{itemize}
		%\vspace{0.02in}
		%\item Bayesian inverse problems governed by PDEs (preliminaries)
		\vspace{0.02in}
		\item Exploiting structured low-rank properties of (Bayesian) inverse problems governed by PDEs
		\vspace{0.02in}
		\begin{itemize}
			\setlength\itemsep{1.0em}
			\item (Global) low rank approximation
			\vspace{0.02in}
			\item Hierarchical off-diagonal low rank (HODLR) approximation
			\vspace{0.02in}
			\item A local point spread function method as a means for efficient
			$\mathcal{H}$ierarchical-matrix approximation
		\end{itemize}
		\vspace{0.02in}
		\item Example: Inversion for the basal friction
		coefficient field in an ice sheet flow problem
		\vspace{0.02in}
		\item Conclusions
	\end{itemize}

>>>>

% title, authors, etc:
\title[Local PSF high-rank Hessian approximation]{Local Point Spread Function Approximation of High-Rank Hessians in Inverse Problems Governed by	PDEs\thanks{Research supported
    partially by NSF-DMS-CAREER-1654311, NSF-DMS-184026 and NSF-OAC-1550547.}}
%\author[{Noemi
%    Petra}]{No\'{e}mi~Petra\inst{1}}

@@

	\begin{itemize}
		\setlength\itemsep{1.0em}
		\item Motivation
		\vspace{0.02in}
		\begin{itemize}
			\setlength\itemsep{1.0em}
			\item Predictive continental scale ice sheet models for anticipating future sea level rise with quantified uncertainties
			\vspace{0.02in}
			\item The need to go beyond ``low rank'' Hessian approximations
		\end{itemize}
		%\vspace{0.02in}
		%\item Bayesian inverse problems governed by PDEs (preliminaries)
		\vspace{0.02in}
		\item Exploiting properties of (Bayesian) inverse problems governed by PDEs
		\vspace{0.02in}
		\begin{itemize}
			\setlength\itemsep{1.0em}
			\item Global low rank structure
			\vspace{0.02in}
			\item Hierarchical off-diagonal low rank
		\end{itemize}
				\vspace{0.02in}
	\item A local point spread function method as a means for efficient
	hierarchical-matrix approximation
		\vspace{0.02in}
		\item Example: Inversion for the basal friction
		coefficient field in an ice sheet flow problem
		\vspace{0.02in}
		\item Conclusions
	\end{itemize}
